---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# glmsummary

<!-- badges: start -->
<!-- badges: end -->

The goal of glmsummary is to make it easy extracting model coefficients from
generalized linear models and generalized linear mixed models in a tabular 
output that you can then format appropriately per your publication needs.

## Installation

You can install the development version of glmsummary from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Bokola/glmsummary")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, warning=FALSE}
library(glmsummary)
required_pks <- c("gee")
suppressWarnings(install_load_packages(required_pks))
## basic example code

df <- glmsummary::df
# general estimating equations (independent correlation structure)
mfit_1 = gee(ord_binary ~ dose + weight + litsz + dose2, family = binomial(link = 'logit'),
id = id, corstr = 'independence', data = df)
# general estimating equations (exchangeable correlation structure)
mfit_2 = gee(ord_binary ~ dose + weight + litsz + dose2, family = binomial(link = 'logit'),
id = id, corstr = 'exchangeable', data = df)
# get coefficients
(coef_1 <- model_estimates(mfit_1))

```


